A linearization procedure for constrained multibody systems

### 2012-08-28 PetersonGedeHubbard2012.tex
Added a sentence to results section.

\section{Results}
\label{sec:results}
The linearized equations of motion are
\begin{align}
  \label{eq:state_space_constrained}
  \left[
    \begin{array}{cc}
      \tilde{M}_{qq} & \bm{0}_{n \times o} \\
      \tilde{M}_{uqc} & \tilde{M}_{uuc} \\
      \tilde{M}_{uqd} & \tilde{M}_{uud}
    \end{array}
    \right]
    \left[
      \begin{array}{c}
        \delta \bm{\dot{q}} \\
        \delta \bm{\dot{u}}
      \end{array}
    \right]
   &=
   \left[
     \begin{array}{cc}
       (\tilde{A}_{qq} + \tilde{A}_{qu} C_1 ) C_0 & \tilde{A}_{qu} C_2 \\
       (\tilde{A}_{uqc} + \tilde{A}_{uuc} C_1 ) C_0 & \tilde{A}_{uuc} C_2\\
       (\tilde{A}_{uqd} + \tilde{A}_{uud} C_1 ) C_0 & \tilde{A}_{uud} C_2
     \end{array}
   \right]
    \left[
      \begin{array}{c}
        \delta \bm{q}_i \\
        \delta \bm{u}_i
      \end{array}
    \right]
    +
    \left[
      \begin{array}{c}
        \bm{0}_{(n+m) \times s} \\
        \tilde{B}_{u}
      \end{array}
    \right]
    \delta \bm{r}
\end{align}
Table \ref{table:assumptions} provides the form in which the nonlinear
equations of motion and constraints must be arranged.  Equations
(\ref{eq:quant_to_compute}) provides the bulk of the terms in equation
(\ref{eq:state_space_constrained}); these terms are Jacobian matrices of the
differential equations. Equations (\ref{eq:C_0})-(\ref{eq:C_2}) provide the
terms $C_0$, $C_1$, and $C_2$ which embed the constraints into
(\ref{eq:state_space_constrained}). Finally, the permutation matrices in
equations (\ref{eq:Pq}) and (\ref{eq:Pu}) separate the independent and
dependent speeds.

@@

>>>>

\section{Results}
\label{sec:results}
The linearized equations of motion are
\begin{align}
  \label{eq:state_space_constrained}
  \left[
    \begin{array}{cc}
      \tilde{M}_{qq} & \bm{0}_{n \times o} \\
      \tilde{M}_{uqc} & \tilde{M}_{uuc} \\
      \tilde{M}_{uqd} & \tilde{M}_{uud}
    \end{array}
    \right]
    \left[
      \begin{array}{c}
        \delta \bm{\dot{q}} \\
        \delta \bm{\dot{u}}
      \end{array}
    \right]
   &=
   \left[
     \begin{array}{cc}
       (\tilde{A}_{qq} + \tilde{A}_{qu} C_1 ) C_0 & \tilde{A}_{qu} C_2 \\
       (\tilde{A}_{uqc} + \tilde{A}_{uuc} C_1 ) C_0 & \tilde{A}_{uuc} C_2\\
       (\tilde{A}_{uqd} + \tilde{A}_{uud} C_1 ) C_0 & \tilde{A}_{uud} C_2
     \end{array}
   \right]
    \left[
      \begin{array}{c}
        \delta \bm{q}_i \\
        \delta \bm{u}_i
      \end{array}
    \right]
    +
    \left[
      \begin{array}{c}
        \bm{0}_{(n+m) \times s} \\
        \tilde{B}_{u}
      \end{array}
    \right]
    \delta \bm{r}
\end{align}
Table \ref{table:assumptions} provides the form in which the nonlinear
equations of motion and constraints must be arranged in order to carry out the
linearization procedure.  Equations (\ref{eq:quant_to_compute}) provides the
bulk of the terms in equation (\ref{eq:state_space_constrained}); these terms
are Jacobian matrices of the differential equations. Equations
(\ref{eq:C_0})-(\ref{eq:C_2}) provide the terms $C_0$, $C_1$, and $C_2$ which
embed the constraints into (\ref{eq:state_space_constrained}). Finally, the
permutation matrices in equations (\ref{eq:Pq}) and (\ref{eq:Pu}) separate the
independent and dependent speeds.

@@

The matrices in Equation (\ref{eq:state_space_constrained}) are evaluated at
the point of linearization $\bm{q}=\bm{q}^*, \bm{\dot{q}}=\bm{\dot{q}}^*,
\bm{u}=\bm{u}^*, \bm{\dot{u}}=\bm{\dot{u}}^*$; this point must satisfy the
equations in Table \ref{table:assumptions}, and may or may not be an
equilibrium point.
